---
title: "Thesis_cover_2018_2020"
author: "Nicole"
date: "10/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PREPPING DATA

Clear workspace (if desired/needed)

```{r}
rm(list = ls())
```

Check working directory, set new working directory if needed.

```{r}
getwd()
```

Install packages and load the package libraries. **Once you have installed a package, you only need to load the library for future use.**

```{r}
library("tidyr")
library("dplyr")
library("readr")
library("ggplot2")
library("ggpubr")
#library("nlme")
```

load in each years .csv files containing the data
```{r}
#TH_2018 <- read.csv(file.choose(), header = TRUE)

relcov_08_20 <- read.csv("../Data/LTER_06MAT_relcov_2008_2020.csv", header = TRUE)

relcov_21 <- read.csv("../Data/LTER_06MAT_relcov_2021.csv", header = TRUE)

```

#look at the data to see what it contains -- *make sure the column names in each data set match so they can be merged together*

```{r}
head(relcov_21) #opens first 6 rows
tail(relcov_21) #opens last 6 rows
summary(relcov_21)
str(relcov_21) #tells us what data types (numbers, factors, etc) are in the data frame
```

#Then merge the years together... **all the names of columns need to be exactly the same name (capitalization and spaces included)

```{r}

MyMerge       <- function(x, y){
  df            <- merge(x, y, all = TRUE)
  rownames(df)  <- df$Row.names
  df$Row.names  <- NULL
  return(df)
}
relcov_08_21           <- Reduce(MyMerge, list(relcov_21, relcov_08_20))


write.csv(relcov_08_21, file = "../Derived CSVs/LTER_06MAT_relcov_all.csv")
```

*make sure the \# of Obs in the 1st data set + the 2nd match the \# of obs in the merged data set*

-- Check unique vales in each column to make sure that there are not naming errors --

```{r}

unique(relcov_08_21$species)

```

-- if there are mistakes then rename them using the code below and recheck unique values again to make sure the recode worked and you didn't loose any observations --

```{r}
#naming convention errors 
relcov_08_21$species <- recode(relcov_08_21$species, "bare " = "bare")
relcov_08_21$species <- recode(relcov_08_21$species, "Litter" = "litter")
relcov_08_21$species <- recode(relcov_08_21$species, "Moss" = "moss")
relcov_08_21$species <- recode(relcov_08_21$species, "Lichen " = "lichen")
relcov_08_21$species <- recode(relcov_08_21$species, "Lichen" = "lichen")
relcov_08_21$species <- recode(relcov_08_21$species, "Fr boil" = "frost boil")
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Sal pul" = "St. D. Sal")
relcov_08_21$species <- recode(relcov_08_21$species, "Ev litter" = "Eri vag litter")

#simplify things identified to species level  that shouldn't be 
  #St.D.
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Led Pal" = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "Dead Evrg" = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "Dead Bet" = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Bet" = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Sal" = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Bet." = "St. D")
relcov_08_21$species <- recode(relcov_08_21$species, "St. D. Evrg" = "St. D")  
  #litter
relcov_08_21$species <- recode(relcov_08_21$species, "Eri vag litter" = "litter")
```

Get overall average cover by species for the CT plots 
```{r}
species.avg.ct <- (relcov_08_21) %>%
  filter(plot== "CT")%>%
  group_by(species)%>% 
  summarise(spec.avg = mean(rel.cov, na.rm = TRUE), n = n(), sd = sd(rel.cov, na.rm = TRUE))

write.csv(species.avg.ct, file = "../Derived CSVs/LTER_06MAT_species_avg_allyrs.csv")
```


-- Remove any data that you will not need for the analysis --

```{r}

relcov_08_21 <- relcov_08_21[!relcov_08_21$block == "4", ] 

```

\~vectors for assigning functional groups\~

```{r}

BARE <- c("Bare ground")
DEC <- c("Deciduous shrubs")
EVRG <- c("Evergreen shrubs")
GRASS <- c("Grass")
SED <- c("Sedge")
LICH <- c("Lichen")
LIT <- c("Litter")
MOSS <- c("Moss")
FORB <- c("Forb")
STD <- c("Standing dead")

```


\~subset the dataset by species then reassigned with functional groups

```{r}
bare <- subset(relcov_08_21, species== "bare" |species== "frost boil")
  bare["func.group"] <- BARE

dec <- subset(relcov_08_21, species== "Bet nan"|species== "Vac uli"|species== "Sal pul"|species== "Arc alp"|"Sal phl"|species== "Sal arc"|species== "Sal ret")
  dec["func.group"] <-DEC

evrg <- subset(relcov_08_21, species== "Emp nig"|species== "Led pal"|species=="Vac vit"|species== "Cas tet"|species== "And pol"|species== "Dry int")
  evrg["func.group"] <-EVRG

grass <- subset(relcov_08_21, species== "Cal can" | species== "Grass ex." | species== "Car big" | species== "Arc lat" | species== "Cal lap" | species== "Fes sp.")
 grass["func.group"] <-GRASS

sed <- subset(relcov_08_21, species== "Eri vag")
  sed["func.group"] <-SED

forb <- subset(relcov_08_21, species== "Ped lap"|species== "Pol bis"|species== "Rub cha"|species== "Luz sp."|species== "Pet sp."|species== "Hie alp"|species== "Ped sp."|species== "Arnica sp."|species== "Ste edw"|species== "Pet fri"|species== "Ste lon"|species== "Sau ang"|species== "Hie sp."|species== "Min sp."|species== "Tof sp."|species== "Ste sp."|species== "dicot"|species== "Lag gla"|species== "Sax pun"|species== "Pyr sec"|species== "Equ arv"|species== "Pol viv"|species== "Tof coc"|species== "Pyr sp.")
  forb["func.group"] <-FORB

lich <- subset(relcov_08_21, species== "lichen")
  lich["func.group"] <-LICH  

lit <- subset(relcov_08_21, species== "litter")
  lit["func.group"] <-LIT
  
moss <- subset(relcov_08_21, species== "moss")
  moss["func.group"] <-MOSS
  
std <- subset(relcov_08_21, species== "St. D")
  std["func.group"] <-STD
```

```{r}

MyMerge       <- function(x, y){
  df            <- merge(x, y, all = TRUE)
  rownames(df)  <- df$Row.names
  df$Row.names  <- NULL
  return(df)
}
relcov.func_08_21           <- Reduce(MyMerge, list(bg1, bg2, ds1, ds2, ds3, ds4, ds5, ds6, ds7, es1, es2, es3, es4, es5, es6, gram1, gram2, gram3, forb1, forb2, forb3, forb4, forb5, forb6, forb7, forb8, forb9, forb10, forb11, forb12, forb13, forb14, forb15, forb16, forb17, forb18, forb19, forb20, forb21, forb22, forb23, forb24, lichen, litter, ms, standing.d))


#export this file

write.csv(relcov.func_08_21, file = "../Derived CSVs/LTER_06MAT_relcov_func_all.csv")

```


## Statistics & graphing

\#combine renamed groups

```{r}

#first we must sum the relative cover values across function groups within quadrats
sum.func <- (relcov.func_08_21) %>% group_by(year, block, plot, quad, func.group) %>% summarise_at(vars(rel.cov), list(relcov = sum ), na.rm = TRUE)
```

subset into different years based on \# of quads measured per plot

```{r}

Q4 <- subset(sum.func, year== "2008")
Q5 <- subset(sum.func, year== "2015" | year== "2020")
Q8 <- subset(sum.func, year== "2010" | year== "2011" | year== "2012" | year== "2013" | year== "2014" | year== "2016" | year== "2017" | year== "2018" | year== "2019" |year== "2010" |year== "2021")

```

Calculate stats across quads within plots

```{r}

#Sum across quads in a plot
Q4_sum_avg_quad <- (Q4) %>% group_by(year, block, plot, func.group) %>% summarise_at(vars(relcov), list(sum1 = sum), na.rm = TRUE)

Q5_sum_avg_quad <- (Q5) %>% group_by(year, block, plot, func.group) %>% summarise_at(vars(relcov), list(sum1 = sum), na.rm = TRUE)

Q8_sum_avg_quad <- (Q8) %>% group_by(year, block, plot, func.group) %>% summarise_at(vars(relcov), list(sum1 = sum), na.rm = TRUE)

#Vectors for averages
avg.Q4.quad <- c(Q4_sum_avg_quad$sum1/4)
avg.Q5.quad <- c(Q5_sum_avg_quad$sum1/5)
avg.Q8.quad <- c(Q8_sum_avg_quad$sum1/8)

#creates and fills a new column with the average (by diving that sum by the number of reps specified)
Q4_sum_avg_quad["avg.1"] <-avg.Q4.quad
Q5_sum_avg_quad["avg.1"] <-avg.Q5.quad
Q8_sum_avg_quad["avg.1"] <-avg.Q8.quad

#-------------------------------------------------------------------------------------------------------#
MyMerge       <- function(x, y){
  df            <- merge(x, y, all = TRUE)
  rownames(df)  <- df$Row.names
  df$Row.names  <- NULL
  return(df)
}
Avg.func.quad           <- Reduce(MyMerge, list(Q4_sum_avg_quad, Q5_sum_avg_quad, Q8_sum_avg_quad))

#export this file
write.csv(Avg.func.quad, file = "../Derived CSVs/LTER_06MAT_avg_relcov_quad.csv")
```

Calculate stats across blocks

```{r}

Avg.func.block <- (Avg.func.quad) %>% group_by(year, plot, func.group) %>% summarise_at(vars(avg.1), list(avg.2 = mean, block.sd = sd), na.rm = TRUE)

#export this file
write.csv(Avg.func.block, file = "../Derived CSVs/LTER_06MAT_avg_relcov_block.csv")

```

\#\#line graph \~ average rel.cov

```{r}
#specify factor levels for fertilization and clipping treatments 

Avg.func.block$plot <- factor(Avg.func.block$plot, levels = c("CT", "F2", "F5", "F10"))
Avg.func.block$func.group <- factor(Avg.func.block$func.group, levels = c("Deciduous shrubs", 
                                                                          "Evergreen shrubs", 
                                                                          "Eri vag",
                                                                          "Graminoid",
                                                                          "Forb",
                                                                          "Lichen",
                                                                          "Moss", 
                                                                          "Litter",
                                                                          "Standing dead",
                                                                          "Bare ground"))

#Creates stacked bar graph#
ggplot(data = Avg.func.block, aes(fill=func.group, x = year, y = avg.2)) +
  geom_bar(position="fill", stat="identity")+ #Percent stacked
  #geom_bar(position="stack", stat="identity")+ #Stacked
  scale_fill_manual(" ", values = c(
    "Deciduous shrubs" = "#004c6d",
                                                           #"Deciduous shrubs" = "red",
                                                           "Evergreen shrubs" = "#6996b3",
                                                           "Eri vag" = "#036d3f",
                                                           #"Eri vag" = "red",
                                                           "Graminoid"="#6fa17e",
                                                          #"Graminoid"="red",
                                                           "Forb"="#c4d6c8",
                                                          #"Forb"="red",
                                                           "Lichen"="#f6e8c3",
                                                           "Moss"="#dfc27d",
                                                           "Litter"="#bf812d",
                                                           "Standing dead"="#8c510a",
                                                           "Bare ground" = "#543005"))+
  theme_light()+
  theme(aspect.ratio = 9/18.5)+ #use for vertical stack only
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1))+
  theme(axis.text.y = element_text(color = "black", size = 6))+
  theme( axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"))+
  scale_y_continuous(breaks= c(0, 0.50, 1))+
  theme(plot.title = element_text(hjust = .5))+
  labs(y = "Mean relative cover", x = " ")+ 
  #theme(axis.title.y = element_text(face = "bold"))+
    #theme(axis.title.x = element_text(face = "bold"))+
  #theme(legend.direction="horizontal")+
  #theme(legend.position="bottom")+
  facet_grid(plot ~ .) #vertically stacked

ggsave("../Figures/LTER_06MAT_stacked_bar_cover.jpeg")
```

##STATISTICS

 test for significant differences in rel cover of each species in 2021

used this site (<https://www.scribbr.com/statistics/anova-in-r/>)

```{r}

#subset data by year and living plants
  quad.avg.2021 <- subset(Avg.func.quad, year== "2021") 
  quad.avg.2021.live <- subset(quad.avg.2021, func.group== "Deciduous shrubs" | func.group== "Eri vag" | func.group== "Evergreen shrubs" | func.group== "Forb" | func.group== "Graminoid" | func.group== "Moss" | func.group== "Lichen")
  
  quad.avg.2018 <- subset(Avg.func.quad, year== "2018") 
  quad.avg.2018.live <- subset(quad.avg.2018, func.group== "Deciduous shrubs" | func.group== "Eri vag" | func.group== "Evergreen shrubs" | func.group== "Forb" | func.group== "Graminoid" | func.group== "Moss" | func.group== "Lichen")

  #check only living plants remain 
unique(quad.avg.2021.live$func.group)

```

# ANOVA
```{r}

ANOVA_21<- aov(avg.1 ~ plot + func.group + plot:func.group, data = quad.avg.2021.live)
summary(ANOVA_21)

ANOVA_18<- aov(avg.1 ~ plot + func.group + plot:func.group, data = quad.avg.2018.live)
summary(ANOVA_18)
```

```{r}
#tukey's HSD
      
TukeyHSD(ANOVA_21, which = "func.group")
      
```

## \#\#Scatter plots \~ average rel.cov of species vs other species (all years, not averaged across blocks)

\#first we need to transform the data from long to wide format so that each functional groups rel.cov is in a separate column

```{r}
  #create a column that combines plot and year together to make a new ID for each observation now called "code" BUT also keep     
  #original columns by setting remove=false

  Scat_prep <- Avg.func.quad %>% unite("code", plot:year, remove = FALSE)

  Scat_prep_func <- Scat_prep[c("code", "avg.1", "func.group")]

  Scat_prep_yr_plot <- Scat_prep[c("code", "plot", "year", "block")]

  Scat_yr_plot <- unique(Scat_prep_yr_plot) 

  #Transform from long to wide format

    #install.packages("reshape2")
  library("reshape2")

  Scat_func <- reshape(Scat_prep_func, idvar = "code", timevar = "func.group", direction = "wide")

  MyMerge       <- function(x, y){
  df            <- merge(x, y, all = TRUE)
  rownames(df)  <- df$Row.names
  df$Row.names  <- NULL
  return(df)
  }
  
  wide.Avg.func.quad           <- Reduce(MyMerge, list(Scat_yr_plot, Scat_func))
  
  #replace NA values with 0's
  wide.Avg.func.quad[is.na(wide.Avg.func.quad)] <- 0
  
  #change year to be a character string 
  wide.Avg.func.quad$year <- as.character(wide.Avg.func.quad$year)
  
  write.csv(wide.Avg.func.quad, file = "../Derived CSVs/LTER_06MAT_WIDE_avg_quad.csv")
```

Now make the graphs...

```{r}

#specify factor levels for fertilization
wide.Avg.func.quad$plot <- factor(wide.Avg.func.quad$plot, levels = c("CT","F2","F5","F10"))

###Bet nan VS Eri Vag
ggplot(data = wide.Avg.func.quad, aes(x = `avg.1.Deciduous shrubs`, y = `avg.1.Eri vag`, color = plot)) +
  scale_color_manual(values = c("CT" = "#d8b365", 
                                "F2" = "#41b6c4",
                                "F5" = "#2c7fb8",
                                "F10" = "#253494"))+
  geom_point(aes(shape=year, size = 0.25))+
  scale_shape_manual(values=c(17, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 15))+
  geom_smooth(method = "lm", se = TRUE, aes(fill = plot))+
  scale_fill_manual(values = c("CT" = "#E2C68E", 
                                "F2" = "#83D1D9",
                                "F5" = "#57A3D7",
                                "F10" = "#8A97E2"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  theme(axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1))+
  theme(axis.text.y = element_text(color = "black", size = 8))+
  theme( axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"))+
  scale_y_continuous(breaks= c(0, 0.15, .3))+
  labs(y = "E. vaginatum", x = "Deciduous shrubs")+ 
  theme(axis.title.y = element_text(face = "bold"))+
    theme(axis.title.x = element_text(face = "bold"))+
   #stat_regline_equation(label.x= 0.6, label.y= 0.15)+ #adds regression line
  #stat_cor(aes(label=..rr.label..), label.x=0.6, label.y=.1)+ #adds R2 
  #stat_cor(method = "pearson", label.x = .5, label.y = .25)+ #adds p-value 
  facet_grid(plot ~ .)

ggsave("../Figures/LTER_06MAT_correlation_decshrubs_Evag.jpeg")

```

```{r}
test1 <- subset(wide.Avg.func.quad, plot == "CT")
```



```{r}
###Bet nan VS Eri Vag (not separated by fert treatment )
ggplot(data = wide.Avg.func.quad, aes(x = `avg.1.Deciduous shrubs`, y = `avg.1.Eri vag`)) +
   geom_point()+
  geom_smooth(method = "lm", se = TRUE)+
   stat_regline_equation(label.x= 0.55, label.y= 0.2)+
  stat_cor(aes(label=..rr.label..), label.x=0.6, label.y=.1)+
    stat_cor(method = "pearson", label.x = .5, label.y = .25) #adds p-value 


###Bet nan VS Forbs
ggplot(data = wide.Avg.func.quad, aes(x = `avg.1.Deciduous shrubs`, y = `avg.1.Forb`, color = plot)) +
  scale_color_manual(values = c("CT" = "#d8b365", 
                                "F2" = "#41b6c4",
                                "F5" = "#2c7fb8",
                                "F10" = "#253494"))+
  geom_point()+
  geom_smooth(method = "lm", se = TRUE, aes(fill = plot))+
  scale_fill_manual(values = c("CT" = "#E2C68E", 
                                "F2" = "#83D1D9",
                                "F5" = "#57A3D7",
                                "F10" = "#8A97E2"))+
   stat_regline_equation(label.x= 0.6, label.y= 0.25)+
  stat_cor(aes(label=..rr.label..), label.x=0.6, label.y=.1)+
  facet_grid(plot ~ .)

###Eri vag VS Forbs
ggplot(data = wide.Avg.func.quad, aes(x = `avg.1.Forb`, y = `avg.1.Eri vag`, color = plot)) +
  scale_color_manual(values = c("CT" = "#d8b365", 
                                "F2" = "#41b6c4",
                                "F5" = "#2c7fb8",
                                "F10" = "#253494"))+
  geom_point()+
  geom_smooth(method = "lm", se = TRUE, aes(fill = plot))+
  scale_fill_manual(values = c("CT" = "#E2C68E", 
                                "F2" = "#83D1D9",
                                "F5" = "#57A3D7",
                                "F10" = "#8A97E2"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  theme(axis.text.x = element_text(color = "black", size = 8, angle = 45, hjust = 1))+
  theme(axis.text.y = element_text(color = "black", size = 8))+
  theme( axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"))+
  scale_y_continuous(breaks= c(0, 0.15, .3))+
  labs(y = "E. vaginatum", x = "Forb")+ 
  theme(axis.title.y = element_text(face = "bold"))+
    theme(axis.title.x = element_text(face = "bold"))+
   stat_regline_equation(label.x= 0.2, label.y= 0.15)+ #adds regression line
  stat_cor(aes(label=..rr.label..), label.x=0.2, label.y=.1)+ #adds R2 
stat_cor(method = "pearson", label.x = .2, label.y = .25)+ #adds p-value 
  facet_grid(plot ~ .)
```

## Format data for PC-ORD

"PCORD_func" - functional group listed in wide format with cover listed under it, with "code" defining each sample unit (used as MAIN in PCORD)

"PCORD_yr_plot" - "code" AKA sample unit with other variables "year" and "plot" listed (used as 2nd in PCORD)

```{r}
#create a column that combines plot and year together to make a new ID for each observation now called "code" BUT also keep original columns by setting remove=false

#PCORD_prep <- Avg.func.block %>% unite("code", plot:year, remove = FALSE)
PCORD_prep <- Avg.func.quad %>% unite("code", plot:year, remove = FALSE) #for data not-averaged across blocks

#PCORD_prep_func <- PCORD_prep[c("code", "avg.2", "func.group")]
PCORD_prep_func <- PCORD_prep[c("code", "avg.1", "func.group")] #for data not-averaged across blocks

#PCORD_prep_yr_plot <- PCORD_prep[c("code", "plot", "year")]
PCORD_prep_yr_plot <- PCORD_prep[c("code", "plot", "year", "block")] #for data not-averaged across blocks

PCORD_yr_plot <- unique(PCORD_prep_yr_plot) 

```

\#Transform from long to wide format

```{r}
#install.packages("reshape2")
library("reshape2")

PCORD_WIDE_func <- reshape(PCORD_prep_func, idvar = "code", timevar = "func.group", direction = "wide")

#replace NA's with 0's  
PCORD_WIDE_func[is.na(PCORD_WIDE_func)] <- 0
```

```{r}
#write.csv(PCORD_WIDE_func, file = "func_cover_PCORD_friendly.csv")
write.csv(PCORD_WIDE_func, file = "../Derived CSVs/LTER_06MAT_relcov_QUAD_PCORD_friendly.csv")

#write.csv(PCORD_yr_plot, file = "yr_plot_PCORD_friendly.csv")
write.csv(PCORD_yr_plot, file = "../Derived CSVs/LTER_06MAT_yr_plot_QUAD_PCORD_friendly.csv")

```

Isolate 2008 and 2021 data from data set not averaged across blocks

```{r}

PCORD_yr_plot_2008 <- subset(PCORD_yr_plot, year== 2008) 
PCORD_yr_plot_2021 <- subset(PCORD_yr_plot, year== 2021)

write.csv(PCORD_yr_plot_2008, file = "../Derived CSVs/LTER_O6MAT_yr_plot_QUAD_PCORD_friendly_2008.csv")
write.csv(PCORD_yr_plot_2021, file = "../Derived CSVs/LTER_06MAT_yr_plot_QUAD_PCORD_friendly_2021.csv")

#--------
Avg.func.quad_2008 <- subset(Avg.func.quad, year== 2008) 
Avg.func.quad_2021 <- subset(Avg.func.quad, year== 2021) 

PCORD_prep_2008 <- Avg.func.quad_2008 %>% unite("code", year:plot, remove = FALSE)
PCORD_prep_2021 <- Avg.func.quad_2021 %>% unite("code", year:plot, remove = FALSE)

PCORD_prep_func_2008 <- PCORD_prep_2008[c("code", "avg.1", "func.group")]
PCORD_prep_func_2021 <- PCORD_prep_2021[c("code", "avg.1", "func.group")]

library("reshape2")

PCORD_WIDE_func_2008 <- reshape(PCORD_prep_func_2008, idvar = "code", timevar = "func.group", direction = "wide")
PCORD_WIDE_func_2008[is.na(PCORD_WIDE_func_2008)] <- 0

PCORD_WIDE_func_2021 <- reshape(PCORD_prep_func_2021, idvar = "code", timevar = "func.group", direction = "wide")
PCORD_WIDE_func_2021[is.na(PCORD_WIDE_func_2021)] <- 0

#----------

write.csv(PCORD_WIDE_func_2008, file = "../Derived CSVs/LTER_06MAT_func_cover_QUAD_PCORD_friendly_2008.csv")
write.csv(PCORD_WIDE_func_2021, file = "../Derived CSVs/LTER_06MAT_func_cover_QUAD_PCORD_friendly_2021.csv")

write.csv(PCORD_yr_plot_2008, file = "../Derived CSVs/LTER_06MAT_yr_plot_QUAD_PCORD_friendly_2008.csv")
write.csv(PCORD_yr_plot_2021, file = "../Derived CSVs/LTER_06MAT_yr_plot_QUAD_PCORD_friendly_2021.csv")

```
