---
title: "Sharable site map code"
author: "Nicole Williamson"
date: "3/4/2022"
output:  
html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Install and load in leaflet packedge 
```{r, message=FALSE, warning=FALSE}
library("leaflet")
```

# Basic map example:  

### Load in data 

```{r, message=FALSE, error=FALSE}
toolik_locations <- read.csv("../Data/Toolik_location.csv") #load in file 
```
  
### Create the map 

This will create a basic map with your site locations marked...  

  **NOTE: `popup = ~ Locations` adds labels to the markers when you click on them**  
```{r, message=FALSE}
toolik_locations <- read.csv("../Data/Toolik_location.csv") #load in file 
head(toolik_locations) #inspect file


leaflet(toolik_locations) %>% 
  addTiles() %>% 
  addScaleBar()%>%
  addMarkers(lng = ~Long, lat = ~Lat, popup = ~ Location)
```
  
You can do lots of cool things to customize your map. 

- specify the area of the map that shows automatically 
- change marker colors based on site features 
- change marker icon to a personalized image
- add a scale bar
- add a legend 
- customize marker labels and embed links 
  - you could potentially embed a link to data generated from that site  
  


### Hope you find this helpful!

