---
title: "Sharable site map code"
author: "Nicole Williamson"
date: "3/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library("xfun")
```

```{r, include=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```


## Install and load in leaflet packedge 
```{r, message=FALSE, warning=FALSE}
library("leaflet")
```

# Basic map example:  

### Load in data 

- I embed a download link for my csv file and images so you can download it and use it as a test run if you need practice. It should work with the code below as long as the directories match to where ever you download the data to.
```{r, echo=FALSE}
xfun::embed_file('../Data/Toolik_location.csv', text = 'Download loaction data HERE')
```
  
```{r, echo=FALSE}
xfun::embed_files(c('../Images/b1.png', '../Images/b2.png', '../Images/b3.png'), text = 'Download icon images HERE')
```

### Create the map 

This will create a basic map with your site locations marked...  

  **NOTE: `popup = ~ Locations` adds labels to the markers when you click on them**  
```{r, message=FALSE}
toolik_locations <- read.csv("../Data/Toolik_location.csv") #load in file 
head(toolik_locations) #inspect file


leaflet(toolik_locations) %>% 
  addTiles() %>% 
  addScaleBar()%>%
  addMarkers(lng = ~Long, lat = ~Lat, popup = ~ Location)
```
  
You can do lots of cool things to customize your map. `r colorize("For more information on how to do these things and more, check out [THIS SITE.](https://rstudio.github.io/leaflet/)", "red")`

- specify the area of the map that shows automatically 
- change marker colors based on site features 
- change marker icon to a personalized image
- add a scale bar
- add a legend 
- customize marker labels and embed links 
  - you could potentially embed a link to data generated from that site  
  
`r colorize("**If you figure out how to do different colors for different sites or any other cool customizations I would love to see it! I want to assign a different custom icon (the icon images I embeded earlier) to each of my sites but I cant figure out how to do it. So if you do anything similar, please share! :) **", "Blue")`  


### Hope you find this helpful!


